Complexity analysis and a fully polynomial-time approximation scheme for the college application problem

### 2022-07-01 paper/paper.tex
wording

\subsection{Literature review}
One way of thinking about the college application problem is as a static variant of the Pandora's Box problem proposed by Weitzman (1979). In a Pandora's Box formulation of college application, the student applies to schools one by one, each time paying the application fee and observing her admissions outcome after a time delay. The problem is to determine an optimal \emph{stopping policy} for when Pandora should halt her college search and accept the best admissions offer she has on hand. Weitzman showed that the optimal policy is to halt the search when the difference between the value of current best offer and the maximum \emph{reservation price,} a statistic over the set of colleges to which Pandora has not yet applied, is positive.

>>>>

\subsection{Literature review}
One way of thinking about the college application problem is as a static variant of the Pandora's Box problem proposed by Weitzman (1979). In a Pandora's Box formulation of college application, the student applies to schools one by one, each time paying the application fee and observing her admissions outcome after a time delay. The problem is to determine an optimal \emph{stopping policy} for when Pandora should halt her college search and accept the best admissions offer she has on hand. Weitzman showed that the optimal policy is to halt the search when the value of the current best offer exceeds the maximum \emph{reservation price,} a certain statistic over the set of colleges to which Pandora has not yet applied.
